### 2017-03-06 README.Rmd
updated README

>>>>

## Random forest example

As a quick example, we'll fit a random forest to the famous Boston housing data included with the package. In fact the original motivation for this package was to be able to compute two-predictor partial dependence plots from random forest models in R.

```{r, fig.width=8, fig.height=4, message=FALSE}
# Fit a random forest to the boston housing data
library(randomForest)  # install.packages("randomForest")
data (boston)  # load the boston housing data
set.seed(101)  # for reproducibility
boston.rf <- randomForest(cmedv ~ ., data = boston)

# Partial dependence of cmedv on lstat and rm
library(pdp)
pd <- partial(boston.rf, pred.var = c("lstat", "rm"), chull = TRUE)
head(pd)  # print first 6 rows

# Lattice version
p1 <- plotPartial(pd)

# ggplot2 version
library(ggplot2)
p2 <- autoplot(pd, contour = TRUE, legend.title = "Partial\ndependence")

# Show both plots in one figure
grid.arrange(p1, p2, ncol = 2)
```
